Spin canonical divisors of log stacky curves

### 2015-06-25 stacky_write_up/spin_cring.tex
switching todos

\begin{lem}
\label{lem:deg1-sat-ind}
Let $X$ be a genus $g$ curve with a $\mathbb{Q}$-divisor $D$ (as
defined by O'Dorney \todo{reference this-Section 1 of Evan's paper, or preferably define it in the background section})
satisfying $h^0(X, \lfloor{D}\rfloor)\ge 1$.  Suppose $P$ is not a base-point of $dD$ for all $d\in \mathbb{N}^+$ meaning that $R_D$ has generically chosen generators (in the appropriate respective degrees)
$u, x_1, \ldots, x_m$ all with $\ord_P(u) =0$ \todo{Aaron: Instead of having $\deg u = 0$, don't we only need that $\ord_P(u) = \lfloor D|_P \rfloor$?} and $\deg(u)=1$. Let $D$ be generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated
in degree at most $\bar{\tau}$, where all $x_i$ also satisfy $\ord_P(u)(x_i)$. \todo{Aaron: What does $\ord_P(u)(x_i)$ mean?}  Suppose $D' = D + \frac{\alpha}{\beta} P$
for some $\alpha,\beta \in \mathbb{N}$ such that
\begin{equation}
\label{eqn:deg1_sat_ind_dim}
	h^0(X, \lfloor{dD + d\frac{\alpha}{\beta} P \rfloor}) = h^0(X,\lfloor dD
	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \; \forall d \in \mathbb{
	N} : d \ge \frac{\beta}{\alpha}.
\end{equation}
\label{eqn:deg1-sat-ind}
Let 
\[
	0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}
\]
be the non-negative best lower approximation.
Then 
\begin{itemize}
\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
degree $d_i$ and has a pole at $P$ of degree $c_i$

@@

If $\Delta > 0$, we must have $\Delta \geq 2$. In this case, let $L_X \in \di X$ be so that $2L_X \sim K_X + \Delta$. We have $\deg L_X \geq 1$, so, by Riemann--Roch, $h^0(\sx,L) \geq 1.$ Therefore, $L$ is linearly equivalent to an effective divisor, so without loss of generality, we may assume $L$ is an effective divisor. We know the theorem holds for $L' = 0$ by Example ~\ref{eg:base-1-0}.
\todo{fix this to accomodate the possibility that $P \in supp(L')$, this has already been done suppose ~\ref{lem:deg1-sat-ind} accommodates it}

@@

\todo{Aaron: It becomes a bit tedious for this proof to alternatingly cite ~\ref{lem:admissible_subset} and ~\ref{thm:ram_order_ind} is there a reason these were separated/can we merge the back together?}
Second, we deal with the case that $\sx$ has at least two stacky points. If $(\sx',\Delta,L')$ is a spin canonical curve so that $L' = P - Q + \frac{1}{3}P_1+ \frac{1}{3}P_2$, then, by Example ~\ref{eg:base-1-33}, it follows that $(\sx', \{3,3\})$ is admissible and satisfies the hypotheses of Theorem ~\ref{thm:ram_order_ind}. Therefore, applying Lemma ~\ref{lem:n-3s-admissible} $r-2$ times, we see that for $(\sx',\Delta',L')$ with $L' = P - Q + \sum_{i=1}^{r}\frac{1}{3}P_i,$ the pair $(\sx',\{3,\ldots, 3\})$ is admissible. Assume for convenience that $e_1 \leq e_2 \leq \cdots \leq e_r$. Applying Theorem ~\ref{thm:ram_order_ind} $\frac{e_1-3}{2}$ times, and letting $J_1 = \{e_1,\ldots, e_1\}$ so that $\# J_1 = r$, we obtain that the theorem holds for $(\sx',\Delta',L')$ with $L' = P - Q + \sum_{i=1}^{r}\subhalf{e_1}P_i,$ and that $(\sx',J_1)$ is admissible. Hence, by Lemma ~\ref{lem:admissible_subset}, it follows that $(\sx',J')$ is admissible, with $J' \subset \{e_1,\ldots, e_1\},$ with $\# J' = r-1$. Then, applying Theorem ~\ref{thm:ram_order_ind} $\frac{e_2-e_1}{2}$ times, and letting $J_2 = \{e_2,\ldots, e_2\}$ so that $\# J_2 = r-1$, we obtain that the theorem holds for $(\sx',\Delta',L')$ with $L' = P - Q + \subhalf{e_1}P_1 + \sum_{i=2}^{r}\subhalf{e_2}P_i,$ and that $(\sx',J_1)$ is admissible. Continuing to altenatively apply Lemma ~\ref{lem:admissible_subset} and Theorem ~\ref{thm:ram_order_ind}, we eventually obtain the theorem holds for $L' = P-Q + \sum_{i=1}^{r}\subhalf {e_i}P_i$, as desired.

>>>>

\begin{lem}
\label{lem:deg1-sat-ind}
Let $X$ be a genus $g$ curve with a $\mathbb{Q}$-divisor $D$ (as
defined by O'Dorney \todo{reference this-Section 1 of Evan's paper, or preferably define it in the background section})
satisfying $h^0(X, \lfloor{D}\rfloor)\ge 1$.  Suppose $P$ is not a base-point of $dD$ for all $d\in \mathbb{N}^+$ meaning that $R_D$ has generically chosen generators (in the appropriate respective degrees)
$u, x_1, \ldots, x_m$ all with $\ord_P(u) =0$ \todo{Aaron: Instead of having $\deg u = 0$, don't we only need that $\ord_P(u) = \lfloor D|_P \rfloor$?} and $\deg(u)=1$. Let $D$ be generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated
in degree at most $\bar{\tau}$, where all $x_i$ also satisfy $\ord_P(u)(x_i)$. \todo{Aaron: What does $\ord_P(u)(x_i)$ mean?}  Suppose $D' = D + \frac{\alpha}{\beta} P$
for some $\alpha,\beta \in \mathbb{N}$ such that
\begin{equation}
\label{eqn:deg1_sat_ind_dim}
	h^0(X, \lfloor{dD + d\frac{\alpha}{\beta} P \rfloor}) = h^0(X,\lfloor dD
	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \text{ for all } d \in \mathbb{
	N} \text{ such that } d \ge \frac{\beta}{\alpha}.
\end{equation}
\label{eqn:deg1-sat-ind}
Let 
\[
	0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}
\]
be the non-negative best lower approximation.
Then 
\begin{itemize}
\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
degree $d_i$ and has a pole at $P$ of degree $c_i$

@@

If $\Delta > 0$, we must have $\Delta \geq 2$. In this case, let $L_X \in \di X$ be so that $2L_X \sim K_X + \Delta$. We have $\deg L_X \geq 1$, so, by Riemann--Roch, $h^0(\sx,L) \geq 1.$ Therefore, $L$ is linearly equivalent to an effective divisor, so without loss of generality, we may assume $L$ is an effective divisor. We know the theorem holds for $L' = 0$ by Example ~\ref{eg:base-1-0}.
\todo{fix this to accomodate the possibility that $P \in supp(L')$, this has already been done suppose ~\ref{lem:deg1-sat-ind} accommodates it. }

@@

\todo{Aaron: It becomes a bit tedious for this proof to alternatingly cite ~\ref{lem:admissible_subset} and ~\ref{thm:ram_order_ind} is there a reason these were separated/can we merge the back together? Better yet, this should probably be a corollary somewhere, since we have to use this implicitly in all three genus cases.}
Second, we deal with the case that $\sx$ has at least two stacky points. If $(\sx',\Delta,L')$ is a spin canonical curve so that $L' = P - Q + \frac{1}{3}P_1+ \frac{1}{3}P_2$, then, by Example ~\ref{eg:base-1-33}, it follows that $(\sx', \{3,3\})$ is admissible and satisfies the hypotheses of Theorem ~\ref{thm:ram_order_ind}. Therefore, applying Lemma ~\ref{lem:n-3s-admissible} $r-2$ times, we see that for $(\sx',\Delta',L')$ with $L' = P - Q + \sum_{i=1}^{r}\frac{1}{3}P_i,$ the pair $(\sx',\{3,\ldots, 3\})$ is admissible. Assume for convenience that $e_1 \leq e_2 \leq \cdots \leq e_r$. Applying Theorem ~\ref{thm:ram_order_ind} $\frac{e_1-3}{2}$ times, and letting $J_1 = \{e_1,\ldots, e_1\}$ so that $\# J_1 = r$, we obtain that the theorem holds for $(\sx',\Delta',L')$ with $L' = P - Q + \sum_{i=1}^{r}\subhalf{e_1}P_i,$ and that $(\sx',J_1)$ is admissible. Hence, by Lemma ~\ref{lem:admissible_subset}, it follows that $(\sx',J')$ is admissible, with $J' \subset \{e_1,\ldots, e_1\},$ with $\# J' = r-1$. Then, applying Theorem ~\ref{thm:ram_order_ind} $\frac{e_2-e_1}{2}$ times, and letting $J_2 = \{e_2,\ldots, e_2\}$ so that $\# J_2 = r-1$, we obtain that the theorem holds for $(\sx',\Delta',L')$ with $L' = P - Q + \subhalf{e_1}P_1 + \sum_{i=2}^{r}\subhalf{e_2}P_i,$ and that $(\sx',J_1)$ is admissible. Continuing to altenatively apply Lemma ~\ref{lem:admissible_subset} and Theorem ~\ref{thm:ram_order_ind}, we eventually obtain the theorem holds for $L' = P-Q + \sum_{i=1}^{r}\subhalf {e_i}P_i$, as desired.
